Person with advantage functionality for `hyper3` objects: `pwa3()`

### 2025-12-07 inst/pwa3.Rmd
pwa3() formalism

```{r}
pwa3
```

@@

  race_help <- 
    race(c("a","c","d","b")) |> pwa3("b", lambda) + 
    race(c("c","d","b","a")) |> pwa3("b", lambda) + 
    race(c("d","c","a","b")) |> pwa3("b", lambda)

@@

```{r calclamf, cache=TRUE}
l <- exp(seq(from=log(0.0002), to=log(2), len=7))
like <- sapply(l,lam)
```

@@

```{r showroots}
lower
upper
```

```{r plotlamf, echo=TRUE,fig.cap="Log-likelihood function for lambda"}
plot(log(l), like - optimal_sol$objective, type='b')
abline(h = c(0, -2))
abline(v = log(optimal_sol$maximum))
abline(v = 0)
segments(x0 = log(c(lower$root, upper$root)), y0 = -2.25, y1 = -1.75, col='gray')
```

Figure \@ref(fig:plotlamf) shows

>>>>

```{r}
pwa3
pwa3_single
```

@@

  race_help <- 
    race(c("a","c","d","b")) |> pwa3(b = lambda) + 
    race(c("c","d","b","a")) |> pwa3(b = lambda) + 
    race(c("d","c","a","b")) |> pwa3(b = lambda)

@@

```{r calclamf, cache=TRUE}
l <- exp(seq(from=log(0.0002), to=log(2), len=17))
like <- sapply(l,lam)
```

@@

```{r plotlamf, echo=TRUE,fig.cap="Log-likelihood function for lambda"}
plot(log(l), like - optimal_sol$objective,
	     type='b', pch=16,
	     xlab = expression(log(lambda)),
	     ylab = "log-likelihood")
abline(h = c(0, -2))
abline(v = log(optimal_sol$maximum))
abline(v = 0)
segments(x0 = log(c(lower$root, upper$root)), y0 = -2.25, y1 = -1.75, col='gray')
```

Figure \@ref(fig:plotlamf) shows a log-likelihood function for
$\log\lambda$.  We see that the evaluate is about
$\lambda=\exp(`r round(log(optimal_sol$maximum),2)`)\simeq
`r round(optimal_sol$maximum,3)`$.  Further, the support interval
runs from about
$\exp(`r round(log(lower$root),2)`)\simeq `r round(lower$root,6)`$
to about
$\exp(`r round(log(upper$root),2)`)\simeq `r round(upper$root,2)`$
thereby excluding the null of $\lambda=1$
which has a support of about `r round(lam(1)-optimal_sol$objective,2)`.
